Lifting CDCL to Relational Domains

### 2016-10-12 example.tex
Related work

\section{Motivating Example}
%
\begin{figure}[t]
\scriptsize
\begin{tabular}{l|l|l}
\hline
C program & Control-Flow Graph & Abstract Conflict Graph \\
\hline
\begin{lstlisting}[mathescape=true,language=C]
void main() {
int x,sepc=0,impl=0;
assume(x>=1 && x<=N);
spec = 2*x; 
int state = 1;
int y=x;
while(state!=0) {
 switch(state) {
  case 0: state = 1; 
  break;
  case 1: state = 2; 
  break;
  case 2: x--; y++;
  if(x == 0) state=0;
  else state=1;break;
 } 
}
impl = y;
assert(spec == impl);
}
\end{lstlisting}
&
\begin{minipage}{4.40cm}
\centering
\vspace*{0.3cm}
\scalebox{.45}{\import{figures/}{example.pspdftex}}
%\caption{A control flow graph for P, P' and abstract conflict graph (ACFG) \label{fig:filter}}
\end{minipage}
&
\begin{minipage}{4.40cm}
\centering
\vspace*{0.3cm}
\scalebox{.45}{\import{figures/}{acdl_run.pspdftex}}
%\caption{A control flow graph for P, P' and abstract conflict graph (ACFG) \label{fig:filter}}
\end{minipage}
\\
\hline
\end{tabular}
\caption{C Program, CFG and Abstract Conflict Graph}
\label{example}
\end{figure}
Let us consider a simple program in Figure~\ref{example} that checks 
the equivalence of a state-machine based interger multiplication against  
a specification that uses multiplication operator (*).  The assertion 
simply compares the result of two multiplication for an integer input $x$.  
To avoid overflow error, we assume $x$ has an upper bound $N$.  The 
control flow graph is shown in the middle column of Figure~\ref{example}.

@@

Hence, ACDCL makes an arbitrary decision $x:[-\infty,1]$ to refine the analysis.  
The decision constrains the interval of $x$.  The deductions made during fixed point
iteration are represented by abstract conflict graph in right-side of 
figure~\ref{example}.   Nodes in the graph denotes the corresponding 
updates to the program variables in the cfg.  Interval analysis concludes 
that the $(n12:\bot)$, that is the decision $x:[-\infty,1]$ leads to a 
{\em conflict}. Intuitively, it means that the program is {\em safe} for 
$x:[-\infty,1]$.

>>>>

\section{Motivating Example}
%
\begin{figure}[t]
\scriptsize
\begin{tabular}{l|l|l}
\hline
C program & Control-Flow Graph & Abstract Conflict Graph \\
\hline
\begin{lstlisting}[mathescape=true,language=C]
void main() {
int x,sepc=0,impl=0;
assume(x>=1 && x<=N);
spec = 2*x; 
int state = 1;
int y=x;
while(state!=0) {
 switch(state) {
  case 0: state = 1; 
  break;
  case 1: state = 2; 
  break;
  case 2: x--; y++;
  if(x == 0) state=0;
  else state=1;break;
 } 
}
impl = y;
assert(spec == impl);
}
\end{lstlisting}
&
\begin{minipage}{4.40cm}
\centering
\vspace*{0.3cm}
\scalebox{.45}{\import{figures/}{example.pspdftex}}
%\caption{A control flow graph for P, P' and abstract conflict graph (ACFG) \label{fig:filter}}
\end{minipage}
&
\begin{minipage}{4.40cm}
\centering
\vspace*{0.3cm}
\scalebox{.45}{\import{figures/}{acdl_run.pspdftex}}
%\caption{A control flow graph for P, P' and abstract conflict graph (ACFG) \label{fig:filter}}
\end{minipage}
\\
\hline
\end{tabular}
\caption{C Program, Control-flow Graph (CFG) and Abstract Conflict Graph}
\label{example}
\end{figure}
Let us consider a simple program in Figure~\ref{example} that checks 
the equivalence of a state-machine based interger multiplication against  
a specification that uses multiplication operator (*).  The assertion 
simply compares the result of two multiplication for an integer input $x$.  
To avoid overflow error, we assume $x$ has an upper bound $N$.  The 
control flow graph is shown in the middle column of Figure~\ref{example}.

@@

Hence, ACDCL makes a decision $x:[-\infty,1]$ to refine the analysis.  
The branching variable $x$ is chosen by an {\em ordered} decision 
heuristics that choose variables appearing in conditional branches 
(assume statement here) first before choosing other program variables. 
The decision constrains the interval of $x$.  The deductions made 
during fixed point iteration are represented by abstract conflict 
graph in right-side of figure~\ref{example}.  Nodes in the graph 
denotes the corresponding updates to the program variables in 
the CFG.  Interval analysis concludes that the $(n12:\bot)$, that 
is the decision $x:[-\infty,1]$ leads to a {\em conflict}.  Thus, 
the program is {\em safe} for $x:[-\infty,1]$.

### 2016-10-12 introduction.tex
example added
Related work

\section{Introduction}
%
Static program analysis based on abstract 
interpretation~\cite{DBLP:conf/emsoft/Cousot07} has been widely used to
verify certain classes of properties for safety-critical systems.  A 
standard static analyses~\cite{se2011} for program safety aims to compute 
invariants by applying transformers that refines an abstract 
value.  Most lattice structure used in static analysis have 
meet and join operations but lack negations.  The meet operation 
precisely model conjunction, and the join operation over-approximate 
disjunction. Thus, the precision loss in static analyzers is often 
due to imprecise join operations. The loss in precision is overcome 
by using richer abstract domains or equipping the analysis with disjunction --
which is often very expensive since the analysis exhibit case enumeration 
behavior.

@@

The instantiation of ACDCL has so far been limited to interval domains only.  
In this paper, we identify specific properties of the CDCL algorithm that 
are necessary to lift the propositional skeleton of CDCL to other richer 
lattice structures and relational abstract domains such as octagons, 
polyhedra, zones and equalities.  To this end, we present a 
characterization of abstract model search procedure and conflict 
analysis procedure that lift the abstract deduction transformer and the 
first-UIP algorithm to relational lattice structures.

>>>>

\section{Introduction}
%
Static program analysis based on abstract 
interpretation~\cite{DBLP:conf/emsoft/Cousot07} has been widely used to
verify certain classes of properties for safety-critical systems.  A 
standard static analyses~\cite{se2011} for program safety aims to compute 
invariants as fixed-points of abstract transformers.  Most lattice structure 
used in static analysis have meet and join operations.  The meet operation 
precisely model conjunction, and the join operation over-approximate 
disjunction. Thus, the precision loss in static analyzers is often 
due to imprecise join operations. The loss in precision is overcome 
by using richer abstract domains or equipping the analysis with disjunction --
which is often very expensive since the analysis exhibit case enumeration 
behavior.

@@

\rmcmt{cite Natural-domain SMT}
\rmcmt{relational domains}

The instantiation of ACDCL has so far been limited to interval domains only.  
In this paper, we identify specific properties of the CDCL algorithm that 
are necessary to lift the propositional skeleton of CDCL to relational 
abstract domains such as template polyhedra domains~\cite{sriram} (octagons, zones and 
equalities).  To this end, we present a characterization of abstract 
model search procedure and conflict analysis procedure that lift 
the abstract deduction transformer and the first-UIP algorithm to 
relational lattice structures.
